Converting LaTeX Legacy R Journal Articles into R Markdown Articles using texor and rebib

### 2023-08-25 texor.tex
pandoc citation

The decision to convert to R Markdown format means that the final output to PDF and HTML will depend on Pandoc (MacFarlane 2023). Pandoc is a versatile document conversion program written in Haskell that is core to numerous documentation systems, including R Markdown and Quarto. Pandoc first converts a document into an abstract syntax tree. From this, it can convert to a different format, including custom ones.

@@

\leavevmode\vadjust pre{\hypertarget{ref-pandoc}{}}%
MacFarlane, John. 2023. {``Pandoc: A Universal Document Converter.''} https://pandoc.org.

>>>>

The decision to convert to R Markdown format means that the final output to PDF and HTML will depend on Pandoc (MacFarlane, Krewinkel, and Rosenthal 2023). Pandoc is a versatile document conversion program written in Haskell that is core to numerous documentation systems, including R Markdown and Quarto. Pandoc first converts a document into an abstract syntax tree. From this, it can convert to a different format, including custom ones.

@@

\leavevmode\vadjust pre{\hypertarget{ref-pandoc}{}}%
MacFarlane, John, Albert Krewinkel, and Jesse Rosenthal. 2023. {``Pandoc.''} https://github.com/jgm/pandoc.
